### 2016-02-28 config/styles.inc.tex
Atually include figures + text from CH04

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
\pgfplotsset{every axis post/.style={unbounded coords=jump}}

@@

\definecolor{model}{named}{blue}
\definecolor{truesys}{named}{TangoAluminium5}

@@

@@

@@

%% interpolation figure

\pgfplotsset{continuous/.style={line width=0.75pt,mark options={solid},mark size=3pt}}
\pgfplotsset{first/.style={color=first,continuous}}
\pgfplotsset{second/.style={color=second,continuous}}
\pgfplotsset{third/.style={color=third,continuous}}
\pgfplotsset{fourth/.style={color=fourth,continuous}}
\pgfplotsset{fifth/.style={color=fifth,continuous}}
\pgfplotsset{sixth/.style={color=sixth,continuous}}

>>>>

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
\pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}

@@

\definecolor{model}{named}{blue}
\definecolor{truesys}{named}{TangoAluminium5}
% \definecolor{truesys}{named}{TangoAluminium4} % from LRMHinf paper

@@

\definecolor{LRM}{named}{TangoScarletRed3}
\definecolor{LPM}{named}{TangoSkyBlue2}
\definecolor{SA}{named}{TangoChameleon2}

\definecolor{validation}{named}{TangoChameleon2}

\definecolor{LPMshade}{named}{TangoSkyBlue1}
\definecolor{LRMshade}{named}{TangoScarletRed1}
\definecolor{refColor}{named}{TangoAluminium6}

\definecolor{frf}{named}{TangoButter3} %TODO: replace
\definecolor{param}{named}{TangoScarletRed2}

@@

%% Initial values

@@

%% LRM chapters

\pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}

\pgfplotsset{hinfnorm/.style={dashed}}
\pgfplotsset{interpol/.style={sharp plot,solid,mark options={solid}}}

\pgfplotsset{LRMgrid/.style={color=LRM,mark size=1.5pt,only marks,mark=square*,mark options={solid}}}
\pgfplotsset{LPMgrid/.style={color=LPM,mark size=1.5pt,only marks,mark=*,mark options={solid}}}
\pgfplotsset{SAgrid/.style={color=SA,densely dotted,solid,mark=triangle*,mark size=1.5pt,mark options={solid}}}

\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=0.2pt}} %TODO: replace

\pgfplotsset{paramPhat/.style={color=param,solid,line width=1.2pt}}

\pgfplotsset{validation/.style={color=validation,densely dotted,mark=diamond*,mark size=1pt,mark options={solid}}}

\pgfplotsset{shaded/.style={opacity=0.5,area legend,solid}}

\pgfplotsset{LPMshade/.style={shaded,fill=LPMshade,draw=LPM}}
\pgfplotsset{LRMshade/.style={shaded,fill=LRMshade,draw=LRM}}

\pgfplotsset{reference/.append style={color=refColor,densely dotted,line width=0.75pt}}
\pgfplotsset{gammafrf/.style={color=black,mark=pentagon,mark options={solid}}}

%% interpolation figure
\pgfplotsset{continuous/.style={line width=0.75pt,mark options={solid},mark size=3pt}}
\pgfplotsset{first/.style={color=first,continuous}}
\pgfplotsset{second/.style={color=second,continuous}}
\pgfplotsset{third/.style={color=third,continuous}}
\pgfplotsset{fourth/.style={color=fourth,continuous}}
\pgfplotsset{fifth/.style={color=fifth,continuous}}
\pgfplotsset{sixth/.style={color=sixth,continuous}}
